Easy as Pi, Volume II: On the Goodput and Energy of Network Coding Schemes in the Raspberry Pi

### 2016-08-16 measurements.tex
more corrections

In Fig.~\ref{fig:enc_ene_rasp1_packet_gf2} and
\ref{fig:enc_ene_rasp1_packet_gf256} for the same device. We exhibit the
relationship between the energy per bit processed on the packet size which
is the inverse of the goodput vs. the packet size scaling law. We set
$g = 128$ in this case to observe energy per bit consumption in the regime where the
processing time is considerable. As we notice again in this case,
$GF(2)$ presents as the field with the smallest energy per bit consumption
given that is the one that has least complex operations. The trends
for the energy can be explained as follows: As the packet size increases,
we process more coded bits at the same time, which increases the encoding
speed, until we hit the critical packet size. After this value, we spend
more time queueing data towards the cache besides the processing, which
increases the time spent per processed bit and thus the energy.
%
\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_v2_Binary_encoder_1600.eps}
        \caption[]%
        {{\small Energy per bit vs. Generation size for $q = 2$}}
        \label{fig:enc_ene_rasp2_gen_gf2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_v2_Binary8_encoder_1600.eps}
        \caption[]%
        {{\small Energy per bit vs. Generation size for $q = 2^8$}}
        \label{fig:enc_ene_rasp2_gen_gf256}
    \end{subfigure}
    \vskip\baselineskip
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_v2_Binary_encoder_128.eps}
        \caption[]%
        {{\small Energy per bit vs. Packet size for $q=2,\ g=128$}}
        \label{fig:enc_ene_rasp2_packet_gf2}
    \end{subfigure}
    \quad
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_v2_Binary8_encoder_128.eps}
        \caption[]%
        {{\small Energy per bit vs. Packet size for $q=2^8,\ g=128$}}
        \label{fig:enc_ene_rasp2_packet_gf256}
    \end{subfigure}
    \caption[]
    {\small Encoder energy measurements for the \ac{Raspi} 2}
    \label{fig:enc_ene_rasp2}
\end{figure*}
%
In Fig.~\ref{fig:enc_ene_rasp2_gen_gf2}, \ref{fig:enc_ene_rasp2_gen_gf256},
\ref{fig:enc_ene_rasp2_packet_gf2} and \ref{fig:enc_ene_rasp2_packet_gf256}
we show the encoding energy per bit consumption for the \ac{Raspi} 2.
We clearly see that the effects discussed for the \ac{Raspi} 1 also apply
as well for the \ac{Raspi} 2. Moreover, given that the average power
is in the same order, but the \ac{Raspi} 2 is a faster device,
the energy costs for the \ac{Raspi} 2 are $2\times$ less than the \ac{Raspi} 1
when referring to variable generation sizes and a fixed packet size.
Furthermore, these costs are 1 order of magnitude less for the \ac{Raspi} 2
with respect to the \ac{Raspi} 1 regarding the case of a fixed generation
size and a variable packet size. This makes the \ac{Raspi} 2 to achieve
a minimum encoding energy consumpiton per bit processed of 0.2 nJ for the
binary field in the mentioned regime.

@@

Some differences occurs due to nature of decoding. In this situation,

>>>>

In Fig.~\ref{fig:enc_ene_rasp1_packet_gf2} and
\ref{fig:enc_ene_rasp1_packet_gf256} for the same device. We exhibit the
relationship between the energy per bit processed on the packet size which
is the inverse of the goodput vs. the packet size scaling law. We set
$g = 128$ in this case to observe energy per bit consumption in the regime where the
processing time is considerable. As we notice again in this case,
$GF(2)$ presents as the field with the smallest energy per bit consumption
given that is the one that has least complex operations. The trends
for the energy can be explained as follows: As the packet size increases,
we process more coded bits at the same time, which increases the encoding
speed, until we hit the critical packet size. After this value, we spend
more time queueing data towards the cache besides the processing, which
increases the time spent per processed bit and thus the energy.
%
\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_v2_Binary_encoder_1600.eps}
        \caption[]%
        {{\small Energy per bit vs. Generation size for $q = 2$}}
        \label{fig:enc_ene_rasp2_gen_gf2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_v2_Binary8_encoder_1600.eps}
        \caption[]%
        {{\small Energy per bit vs. Generation size for $q = 2^8$}}
        \label{fig:enc_ene_rasp2_gen_gf256}
    \end{subfigure}
    \vskip\baselineskip
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_v2_Binary_encoder_128.eps}
        \caption[]%
        {{\small Energy per bit vs. Packet size for $q=2,\ g=128$}}
        \label{fig:enc_ene_rasp2_packet_gf2}
    \end{subfigure}
    \quad
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_v2_Binary8_encoder_128.eps}
        \caption[]%
        {{\small Energy per bit vs. Packet size for $q=2^8,\ g=128$}}
        \label{fig:enc_ene_rasp2_packet_gf256}
    \end{subfigure}
    \caption[]
    {\small Encoder energy measurements for the \ac{Raspi} 2}
    \label{fig:enc_ene_rasp2}
\end{figure*}
%
In Fig.~\ref{fig:enc_ene_rasp2_gen_gf2}, \ref{fig:enc_ene_rasp2_gen_gf256},
\ref{fig:enc_ene_rasp2_packet_gf2} and \ref{fig:enc_ene_rasp2_packet_gf256}
we show the encoding energy per bit consumption for the \ac{Raspi} 2.
We clearly see that the effects discussed for the \ac{Raspi} 1 also apply
as well for the \ac{Raspi} 2. Moreover, given that the average power
is in the same order, but the \ac{Raspi} 2 is a faster device,
the energy costs for the \ac{Raspi} 2 are $2\times$ less than the \ac{Raspi} 1
when referring to variable generation sizes and a fixed packet size.
Furthermore, these costs are one order of magnitude less for the \ac{Raspi} 2
with respect to the \ac{Raspi} 1 regarding the case of a fixed generation
size and a variable packet size. This makes the \ac{Raspi} 2 achieve
a minimum encoding energy consumpiton per bit processed of 0.2 nJ for the
binary field in the mentioned regime.

@@

Some differences occurs due to the nature of decoding. In this situation,
